---
title: "Main effects and interactions at all deciles: examples"
author: "Rand R. Wilcox & Guillaume A. Rousselet"
date: "`r Sys.Date()`"
output:
  pdf_document:
    fig_caption: no
    number_sections: no
    toc: yes
    toc_depth: 2
---

Illustrate simulated examples similar to the ones used in the power simulations. Generate samples at maximum sample size (n=100). Plot marginals, separate shift functions at each level of A, shift functions for main effects and interaction, distributions of all pairwise differences, their quantiles, and their quantile differences (interaction).

Illustrate one example with real data from [Clark et al. (2011)](https://jech.bmj.com/content/66/9/782.long).

# Dependencies

```{r, message=FALSE, warning=FALSE}
library(ggplot2)
library(tibble)
library(cowplot)
source("./code/theme_gar.txt")
source("./code/examples.R") # wrapper + plot functions
source("./code/mainfuns.R")
source("./code/decinter.R")
source("./code/iband.R")
# Compile C++ code:
library(Rcpp)
sourceCpp("./code/dec_apd_all.cpp")
```

# Parameters

```{r}
nboot <- 2000 # bootstrap samples
qseq <- seq(0.1, 0.9, 0.1)
nq <- length(qseq)
alpha.val <- 0.05
probs <- c(alpha.val/2, 1-alpha.val/2) # to compute confidence intervals
n <- 100 # sample size

### Plot parameters
plot_param <- list()
# vertical bars for uncertainty intervals
plot_param$diffint_col <- "black"
plot_param$diffint_size <- 0.75 
plot_param$diffint_col50 <- "black"
plot_param$diffint_size50 <- 2.5 
# line joining the quantiles
plot_param$q_line_col <- "black"
plot_param$q_line_alpha <- 1
plot_param$q_line_size <- 2
# symbols marking the quantiles
plot_param$symb_col <- "black" 
plot_param$symb_size <- 5
plot_param$symb_shape <- 21
plot_param$symb_fill <- "lightgrey" 
```

# Distributions that differ by a constant

The code below can be used to generate data similar to what we used in the simulations in notebooks `sim_tp.Rmd` and `sim_tp_apd.Rmd`. Sampling is from one of four continuous distributions, with groups shifted by a constant.  

## Generate data

```{r}
set.seed(21)

todo <- 1 # [1] norm | [2] cnorm | [3] lnorm | [4] clnorm

if(todo == 1){
  # normal
  rdist <- rnorm
  rdist.name <- "norm"
  gpmeans <- c(0, 0.1, 0.2, 0.8)
  # gpmeans <- c(0, 0.5, 0.3, 1.2)
} else if(todo == 2){
  # contaminated normal
  rdist <- cnorm
  rdist.name <- "cnorm"
  gpmeans <- c(0, 0.1, 0.2, 0.8)
} else if(todo == 3){
  # lognormal
  rdist <- rlnorm
  rdist.name <- "lnorm"
  gpmeans <- c(0, 0, 0.1, 0.5)
} else if(todo == 4){
  # contaminated lognormal
  rdist <- clnorm
  rdist.name <- "clnorm"
  gpmeans <- c(0, 0, 0.1, 0.5)
}

x <- list()
for(C in 1:4){
  x[[C]] <- rdist(n) + rep(gpmeans[C], n)
}
# x <- matrix(data = rdist(n*4), nrow = n) + matrix(data = rep(gpmeans, each = n), nrow = n)
```

## Compute deciles and all comparisons

Compute confidence intervals and p values for all simple effects, main effects and interactions.

```{r}
set.seed(21)
res <- dec_apd_all_wrap(x, nboot, probs)
# this function is the file examples.R
```

## Plot marginal distributions

```{r}
set.seed(21)
pA <- plot_marg(x, res, col = "black")
pA
```

## Plot shift functions at each level of A

### A1: B1-B2

```{r}
pB <- plot_ind_sf_ab(res, plot_param)
pB
```

Thick vertical lines = 50% confidence intervals.  
Thin vertical lines = 1-alpha confidence intervals.  

Check p values
```{r}
res$ab.pv
```

P values corrected for multiple comparisons
```{r}
p.adjust(res$ab.pv, method = "fdr")
```


### A2: B1-B2

```{r}
pC <- plot_ind_sf_cd(res, plot_param)
pC
```

Check p values
```{r}
res$cd.pv
```

P values corrected for multiple comparisons
```{r}
p.adjust(res$cd.pv, method = "fdr")
```

## Plot main effects and interaction

### Main effect of A

```{r}
# x axis: plot mean of quantiles 
# plotx == "mean" 
# or quantiles of observations pooled across 2 levels
# plotx == "pool"
pD <- plot_main_A(res, plot_param, plotx = "pool")
pD
```

Check p values
```{r}
res$mainA.pv
```

P values corrected for multiple comparisons
```{r}
p.adjust(res$mainA.pv, method = "fdr")
```

### Main effect of B

```{r}
pE <- plot_main_B(res, plot_param, plotx = "pool")
pE
```

Check p values
```{r}
res$mainB.pv
```

P values corrected for multiple comparisons
```{r}
p.adjust(res$mainB.pv, method = "fdr")
```

### Interaction

```{r}
pF <- plot_inter(res, plot_param, plotx = "pool")
pF
```

Check p values
```{r}
res$inter.pv
```

P values corrected for multiple comparisons
```{r}
p.adjust(res$inter.pv, method = "fdr")
```

## Plot all pairwise differences + deciles

```{r}
set.seed(21)
pG <- plot_apd(res)
pG
```

## All pairwise differences: interaction

```{r}
pH <- plot_apd_inter(res, plot_param)
pH
```

Check p values
```{r}
res$apd.ab.pv
```

P values corrected for multiple comparisons
```{r}
p.adjust(res$apd.ab.pv, method = "fdr")
```

## Figure with combined panels

```{r, eval=FALSE}
cowplot::plot_grid(pA, pB, pC, pD, pE, pF, pG, pH,
                   labels=c("A", "B", "C", "D", "E", "F", "G", "H"), ncol = 2, nrow = 4,
                   rel_heights = c(1, 1, 1, 1, 1, 1, 1, 1), label_size = 20, hjust = -0.5, scale=.95)
# save figure
ggsave(filename=paste0('./figures/fig_ex_',rdist.name,'.pdf'),width=12,height=15) 
```

# Example with real data

Data are from:

[Clark et al. (2011)](https://jech.bmj.com/content/66/9/782.long)

Clark, F., Jackson, J., Carlson, M., Chou, C.-P., Cherry, B.J., Jordan-Marsh, M., Knight, B.G., Mandel, D., Blanchard, J., Granger, D.A., Wilcox, R.R., Lai, M.Y., White, B., Hay, J., Lam, C., Marterella, A., & Azen, S.P. (2012) Effectiveness of a lifestyle intervention in promoting the well-being of independently living older people: results of the Well Elderly 2 Randomised Controlled Trial. J Epidemiol Community Health, 66, 782–790.

We look at perceived health in older adults, split into 4 groups based on education level and the presence of depressive symptoms.

## Load data

```{r}
dat <- read.table('./data/A1B1C_dat.txt') # todo
# d <- cbind(dat$MAPAGLOB, dat$edugp, dat$BK_SEX)
x <- cbind(dat$pfnbs_s, dat$edugp, dat$CESD)
x <- elimna(x) # remove missing values
# split into groups based on education and CESD score
flag <- x[,3] > 15 
a <- fac2list(x[,1], cbind(x[,2],flag), pr = FALSE) # 
a <- a[c(1,2,5,6)]
# A1B1 = lower education, lower CESD, 
# A1B2 = lower education, higher CESD, 
# A2B1 = higher education, lower CESD, 
# A2B2 = higher education, higher CESD. 
```

## ANOVA on means

### Using t2way
```{r}
t2w.res <- t2way(2,2,a,tr=0)
t2w.res
```

### Using aov
```{r}
df <- tibble(health = as.vector(unlist(a)),
             education = factor(c(rep("lower", length(a[[1]]) + length(a[[2]])), rep("higher", length(a[[3]]) + length(a[[4]])))),
             depression = factor(c(rep("lower", length(a[[1]])), rep("higher", length(a[[2]])), 
                                   rep("lower", length(a[[3]])), rep("higher", length(a[[4]]))))
             )
aov.res <- aov(health ~ education * depression, data = df)
summary(aov.res)
```

## Apply method 1

### Apply function
```{r, eval=FALSE}
set.seed(21)
# use Hochberg's correction
res1 <- decinter(a, method='hoch', SEED=FALSE, nboot=nboot) #default is 'BH'
save(res1, file = "./data/examples_res1.RData")
```

### Check results
```{r}
load(file = "./data/examples_res1.RData")
res1
```

### Use FDR correction
```{r}
p.adjust(res1[,7], method="fdr")
```

## Apply method 2

```{r, eval=FALSE}
set.seed(21)
# use Hochberg's correction
res2 <- iband(a, method='hoch', SEED=FALSE, nboot=nboot) #default is 'BH'
save(res2, file = "./data/examples_res2.RData")
```

### Check results
```{r}
load(file = "./data/examples_res2.RData")
res2
```

### Use FDR correction
```{r}
p.adjust(res2[,7], method="fdr")
```

## Compute deciles and all comparisons

Compute confidence intervals and p values for all simples effects, main effects and interaction. The main calculations are handled by an Rcpp function, which is much faster than the code in base R.

```{r}
set.seed(21)
res <- dec_apd_all_wrap(a, nboot, probs)
```

## Make figures

### Plot marginal distributions

```{r}
set.seed(21)
pA <- plot_marg(a, res, col = "black") + coord_cartesian(ylim = c(0, 65)) +
        labs(y = "Perceived health scores")
pA
```

### Plot shift functions at each level of A

#### A1: B1-B2

```{r}
pB <- plot_ind_sf_ab(res, plot_param)
pB
```

Thick vertical lines = 50% confidence intervals.  
Thin vertical lines = 1-alpha confidence intervals.  
Check p values
```{r}
res$ab.pv
```

P values corrected for multiple comparisons
```{r}
p.adjust(res$ab.pv, method = "fdr")
```

#### A2: B1-B2

```{r}
pC <- plot_ind_sf_cd(res, plot_param)
pC
```

Check p values
```{r}
res$cd.pv
```

P values corrected for multiple comparisons
```{r}
p.adjust(res$cd.pv, method = "fdr")
```

### Plot main effects and interaction

#### Main effect of A

```{r}
# x axis: plot mean of quantiles 
# plotx == "mean" 
# or quantiles of observations pooled across 2 levels
# plotx == "pool"
pD <- plot_main_A(res, plot_param, plotx = "pool")
pD
```

Check p values
```{r}
res$mainA.pv
```

P values corrected for multiple comparisons
```{r}
p.adjust(res$mainA.pv, method = "fdr")
```

#### Main effect of B

```{r}
pE <- plot_main_B(res, plot_param, plotx = "pool")
pE
```

Check p values
```{r}
res$mainB.pv
```

P values corrected for multiple comparisons
```{r}
p.adjust(res$mainB.pv, method = "fdr")
```

#### Interaction

```{r}
pF <- plot_inter(res, plot_param, plotx = "pool")
pF
```

Check p values
```{r}
res$inter.pv
```

P values corrected for multiple comparisons
```{r}
p.adjust(res$inter.pv, method = "fdr")
```

### Plot all pairwise differences + deciles

```{r}
set.seed(21)
pG <- plot_apd(res)
pG
```

### Inferences on the median of the difference scores

"For the second group, testing the hypothesis that the median of the difference scores is zero, the estimate is 10.5, with a [4.2, 14.7] 95% confidence interval, $p=0$. In the first group the median is 4.21 [0, 8.4], $p=0.0765$."

#### Group 1
```{r}
set.seed(44)
wmwpb(a[[1]],a[[2]],est=median,alpha=.05,nboot=2000,SEED=FALSE,pr=FALSE)
```

#### Group 2
```{r}
set.seed(44)
wmwpb(a[[3]],a[[4]],est=median,alpha=.05,nboot=2000,SEED=FALSE,pr=FALSE)
```

### All pairwise differences: interaction

```{r}
pH <- plot_apd_inter(res, plot_param)
pH
```

Check p values
```{r}
res$apd.inter.pv
```

P values corrected for multiple comparisons
```{r}
p.adjust(res$apd.inter.pv, method = "fdr")
```

### Figures with combined panels

#### One large figure
```{r, eval=FALSE}
cowplot::plot_grid(pA, pB, pC, pD, pE, pF, pG, pH,
                   labels=c("A", "B", "C", "D", "E", "F", "G", "H"), ncol = 2, nrow = 4,
                   rel_heights = c(1, 1, 1, 1, 1, 1, 1, 1), label_size = 20, hjust = -0.5, scale=.95)
# save figure
ggsave(filename=paste0('./figures/fig_ex_A1B1C.pdf'),width=12,height=15) 
```

### Split decinter and apdinter results

#### Results: decinter
```{r, eval=FALSE, fig.height = 8}
cowplot::plot_grid(pA, pB, pC, pD, pE, pF,
                   labels=c("A", "B", "C", "D", "E", "F"), ncol = 2, nrow = 3,
                   rel_heights = c(1, 1, 1, 1, 1, 1, 1, 1), label_size = 20, hjust = -0.5, scale=.95)
# save figure
ggsave(filename=paste0('./figures/fig_ex_A1B1C_dec.pdf'),width=12,height=12) 
```

#### Results: apdinter (iband)
```{r, eval=FALSE}
cowplot::plot_grid(pG, pH,
                   labels=c("A", "B"), ncol = 2, nrow = 1,
                   rel_heights = c(1, 1, 1, 1, 1, 1, 1, 1), label_size = 20, hjust = -0.5, scale=.95)
# save figure
ggsave(filename=paste0('./figures/fig_ex_A1B1C_apd.pdf'),width=12,height=4) 
```




