---
title: "Kurtosis estimation"
author: "Rand R. Wilcox & Guillaume A. Rousselet"
date: "`r Sys.Date()`"
output:
  pdf_document:
    fig_caption: no
    number_sections: no
    toc: yes
    toc_depth: 2
    fig_width: 8 
---

Code supporting this statement:

"Consider, for example, a lognormal distribution, which has kurtosis 113.9.
Based on a sample of 100,000, the kurtosis of the lognormal distribution was
estimated and this process was repeated 1000 times. It was found that 79\% of the estimates were less than the true value.
The median estimate was 80. This process was repeated using the contaminated lognormal distribution which is skewed and very heavy-tailed. The kurtosis of this distribution was estimated based on a sample size of one million. This process was
repeated 1000 times yielding estimates ranging between 242 and 16400.
The median estimate was 423."

# Dependencies
```{r, message=FALSE, warning=FALSE}
source("./code/mainfuns.R")
```

# Lognormal simulation

## Get population kurtosis

A *g-and-h* distribution with parameters $g=$1 and $h=$0 has the same shape as a lognormal distribution.
```{r}
lnorm_kurt <- gskew(1)$kurtosis
```

The lognormal distribution has kurtosis = `r round(lnorm_kurt, digits = 1)`.

## Simulation
```{r, eval=FALSE}
set.seed(21)

nsim <- 1000 # number of iterations
nsamp <- 100000 # sample size
sim_lnorm <- vector(mode = "numeric", length = nsim)

for(i in 1:nsim){
  sim_lnorm[i] <- skew(rlnorm(nsamp))$kurtosis
}
save(sim_lnorm, file='./data/sim_lnorm.Rdata')
```

## Results 
```{r}
load(file='./data/sim_lnorm.Rdata')
summary(sim_lnorm)
```

The proportion of estimates less than the true value is `r 100 * mean(sim_lnorm < lnorm_kurt)`%.

# Contaminated lognormal simulation

```{r, eval=FALSE}
set.seed(21)

nsim <- 1000 # number of iterations
nsamp <- 1000000 # sample size
sim_clnorm <- vector(mode = "numeric", length = nsim)

for(i in 1:nsim){
  sim_clnorm[i] <- skew(clnorm(nsamp))$kurtosis
}

save(sim_clnorm, file='./data/sim_clnorm.Rdata')
```

## Results
```{r}
load(file='./data/sim_clnorm.Rdata')
summary(sim_clnorm)
```

