---
title: "Quantile differences between distributions of all pairwise differences: false positives, boot1 vs. boot9"
author: "Rand R. Wilcox & Guillaume A. Rousselet"
date: "`r Sys.Date()`"
output:
  pdf_document:
    fig_caption: no
    number_sections: no
    toc: yes
    toc_depth: 2
    fig_width: 8 
---

Strategy: for each level of A, compute all pairwise differences between B1 and B2. Then compare the quantiles (here deciles) of these two distributions. 

Estimate FWER = probability of at least one false negative among 9 deciles.
Use HD only; compare bootstrap with the same samples for all deciles vs. different samples. Do that for one sample size only. With n=40, the distribution of all pairwise differences = 1600 observations!

# Dependencies

```{r, message=FALSE, warning=FALSE}
library(ggplot2)
library(tibble)
library(beepr)
source("./code/theme_gar.txt")
source("./code/mainfuns.R")
source("./code/plot.R")
# Compile C++ code:
library(Rcpp)
sourceCpp("./code/apdinter_b1b9.cpp")
```

# Parameters

```{r}
nsim <- 10000 # iterations
nboot <- 2000 # bootstrap samples
inc.step <- 500 # console update every inc.step iterations
qseq <- seq(0.1, 0.9, 0.1)
nq <- length(qseq)
alpha.val <- 0.05
ref.fp <- 1-(1-alpha.val)^nq # FWER for uncorrelated comparisons
n <- 40 # unique sample size
# pre-compute the beta weights
hd.w <- hd.w.calc(n*n, qseq)
hd.w <- hd.w[[1]] # one sample size only -- extract here
```

# Normal distributions

```{r, eval=FALSE}
set.seed(21)
rdist <- rnorm
simres <- apdinter_b1b9_sim(rdist, n, hd.w)
save(simres, file = "./data/sim_fp_apd_pval_normal_b1b9.RData")
fwer <- apdinter_b1b9_fwer(simres)
save(fwer, file = "./data/sim_fp_apd_fwer_normal_b1b9.RData")
```

## Results: FWER
```{r}
load(file = "./data/sim_fp_apd_fwer_normal_b1b9.RData")
b1.bt <- binom.test(sum(fwer$AB.b1.fdr), length(fwer$AB.b1.fdr), p = alpha.val)
b9.bt <- binom.test(sum(fwer$AB.b9.fdr), length(fwer$AB.b9.fdr), p = alpha.val)
binodiff <- bi2KMSv2(sum(fwer$AB.b1.fdr), length(fwer$AB.b1.fdr), sum(fwer$AB.b9.fdr), length(fwer$AB.b9.fdr))
```

FWER: boot1 = `r round(b1.bt$estimate, digits=3)` [`r round(b1.bt$conf.int[1], digits=3)`, `r round(b1.bt$conf.int[2], digits=3)`]; boot9 = `r round(b9.bt$estimate, digits=3)` [`r round(b9.bt$conf.int[1], digits=3)`, `r round(b9.bt$conf.int[2], digits=3)`]; difference = `r round(binodiff$est.dif, digits=3)` [`r round(binodiff$ci[1], digits=3)`, `r round(binodiff$ci[2], digits=3)`], *p* = `r binodiff$p.value`.

## Results: individual deciles
```{r}
load(file = "./data/sim_fp_apd_pval_normal_b1b9.RData")
plot.title <- "Normal"
p <- plot_fp_apd_ind_b1b9(simres, plot.title, alpha.val)
p
#ggsave(filename = "./figures/fig_fp_apd_ind_normal_b1b9_test.pdf", width = 8, height = 10)
```

# Lognormal distributions

```{r, eval=FALSE}
set.seed(21)
rdist <- rlnorm
simres <- apdinter_b1b9_sim(rdist, n, hd.w)
save(simres, file = "./data/sim_fp_apd_pval_lognormal_b1b9.RData")
fwer <- apdinter_b1b9_fwer(simres)
save(fwer, file = "./data/sim_fp_apd_fwer_lognormal_b1b9.RData")
```

## Results: FWER
```{r}
load(file = "./data/sim_fp_apd_fwer_lognormal_b1b9.RData")
b1.bt <- binom.test(sum(fwer$AB.b1.fdr), length(fwer$AB.b1.fdr), p = alpha.val)
b9.bt <- binom.test(sum(fwer$AB.b9.fdr), length(fwer$AB.b9.fdr), p = alpha.val)
binodiff <- bi2KMSv2(sum(fwer$AB.b1.fdr), length(fwer$AB.b1.fdr), sum(fwer$AB.b9.fdr), length(fwer$AB.b9.fdr))
```

FWER: boot1 = `r round(b1.bt$estimate, digits=3)` [`r round(b1.bt$conf.int[1], digits=3)`, `r round(b1.bt$conf.int[2], digits=3)`]; boot9 = `r round(b9.bt$estimate, digits=3)` [`r round(b9.bt$conf.int[1], digits=3)`, `r round(b9.bt$conf.int[2], digits=3)`]; difference = `r round(binodiff$est.dif, digits=3)` [`r round(binodiff$ci[1], digits=3)`, `r round(binodiff$ci[2], digits=3)`], *p* = `r binodiff$p.value`.

## Results: individual deciles
```{r}
load(file = "./data/sim_fp_apd_pval_lognormal_b1b9.RData")
plot.title <- "Lognormal"
p <- plot_fp_apd_ind_b1b9(simres, plot.title, alpha.val)
p
#ggsave(filename = "./figures/fig_fp_apd_ind_lognormal_b1b9_test.pdf", width = 8, height = 10)
```

# Contaminated normal distributions

```{r, eval=FALSE}
set.seed(21)
rdist <- cnorm
simres <- apdinter_b1b9_sim(rdist, n, hd.w)
save(simres, file = "./data/sim_fp_apd_pval_cnorm_b1b9.RData")
fwer <- apdinter_b1b9_fwer(simres)
save(fwer, file = "./data/sim_fp_apd_fwer_cnorm_b1b9.RData")
```

## Results: FWER
```{r}
load(file = "./data/sim_fp_apd_fwer_cnorm_b1b9.RData")
b1.bt <- binom.test(sum(fwer$AB.b1.fdr), length(fwer$AB.b1.fdr), p = alpha.val)
b9.bt <- binom.test(sum(fwer$AB.b9.fdr), length(fwer$AB.b9.fdr), p = alpha.val)
binodiff <- bi2KMSv2(sum(fwer$AB.b1.fdr), length(fwer$AB.b1.fdr), sum(fwer$AB.b9.fdr), length(fwer$AB.b9.fdr))
```

FWER: boot1 = `r round(b1.bt$estimate, digits=3)` [`r round(b1.bt$conf.int[1], digits=3)`, `r round(b1.bt$conf.int[2], digits=3)`]; boot9 = `r round(b9.bt$estimate, digits=3)` [`r round(b9.bt$conf.int[1], digits=3)`, `r round(b9.bt$conf.int[2], digits=3)`]; difference = `r round(binodiff$est.dif, digits=3)` [`r round(binodiff$ci[1], digits=3)`, `r round(binodiff$ci[2], digits=3)`], *p* = `r binodiff$p.value`.

## Results: individual deciles
```{r}
load(file = "./data/sim_fp_apd_pval_cnorm_b1b9.RData")
plot.title <- "Contaminated normal"
p <- plot_fp_apd_ind_b1b9(simres, plot.title, alpha.val)
p
#ggsave(filename = "./figures/fig_fp_apd_ind_cnorm_b1b9_test.pdf", width = 8, height = 10)
```

# Contaminated lognormal distributions

```{r, eval=FALSE}
set.seed(21)
rdist <- clnorm
simres <- apdinter_b1b9_sim(rdist, n, hd.w)
save(simres, file = "./data/sim_fp_apd_pval_clnorm_b1b9.RData")
fwer <- apdinter_b1b9_fwer(simres)
save(fwer, file = "./data/sim_fp_apd_fwer_clnorm_b1b9.RData")
```

## Results: FWER
```{r}
load(file = "./data/sim_fp_apd_fwer_clnorm_b1b9.RData")
b1.bt <- binom.test(sum(fwer$AB.b1.fdr), length(fwer$AB.b1.fdr), p = alpha.val)
b9.bt <- binom.test(sum(fwer$AB.b9.fdr), length(fwer$AB.b9.fdr), p = alpha.val)
binodiff <- bi2KMSv2(sum(fwer$AB.b1.fdr), length(fwer$AB.b1.fdr), sum(fwer$AB.b9.fdr), length(fwer$AB.b9.fdr))
```

FWER: boot1 = `r round(b1.bt$estimate, digits=3)` [`r round(b1.bt$conf.int[1], digits=3)`, `r round(b1.bt$conf.int[2], digits=3)`]; boot9 = `r round(b9.bt$estimate, digits=3)` [`r round(b9.bt$conf.int[1], digits=3)`, `r round(b9.bt$conf.int[2], digits=3)`]; difference = `r round(binodiff$est.dif, digits=3)` [`r round(binodiff$ci[1], digits=3)`, `r round(binodiff$ci[2], digits=3)`], *p* = `r binodiff$p.value`.

## Results: individual deciles
```{r}
load(file = "./data/sim_fp_apd_pval_clnorm_b1b9.RData")
plot.title <- "Contaminated lognormal"
p <- plot_fp_apd_ind_b1b9(simres, plot.title, alpha.val)
p
#ggsave(filename = "./figures/fig_fp_apd_ind_clnorm_b1b9_test.pdf", width = 8, height = 10)
```

# Conclusion
No evidence for better performance using separate bootstrap samples for every decile.
Keep using the same bootstrap samples for all deciles for computational efficiency.
Overall the approach is conservative for all distributions. Looking at individual deciles, we're closer to the nominal level nearer the centre of the distribution, a bit conservative at the extremes, but overall close to 0.05.

