---
title: "Quantile differences between distributions of all pairwise differences: true positives"
author: "Rand R. Wilcox & Guillaume A. Rousselet"
date: "`r Sys.Date()`"
output:
  pdf_document:
    fig_caption: no
    number_sections: no
    toc: yes
    toc_depth: 2
---

Estimate power = probability of at least one true positive among 9 deciles.
Use percentile bootstrap with the same samples for all deciles. 
Compare HD to QT7.  
Compare to standard ANOVA on means and 20% trimmed means (no bootstrap).

# Dependencies

```{r, message=FALSE, warning=FALSE}
library(ggplot2)
library(tibble)
library(beepr)
library(cowplot)
source("./code/theme_gar.txt")
source("./code/mainfuns.R")
source("./code/plot.R")
# Compile C++ code:
library(Rcpp)
sourceCpp("./code/apdinter_hdqt7.cpp")
```

# Parameters

```{r}
nsim <- 10000 # iterations
nboot <- 2000 # bootstrap samples
inc.step <- 500 # console update every inc.step iterations
qseq <- seq(0.1, 0.9, 0.1)
nq <- length(qseq)
alpha.val <- 0.05
ref.fp <- 1-(1-alpha.val)^nq # FWER for uncorrelated comparisons
nseq <- seq(20, 100, 10) # sample sizes
nmax <- max(nseq) # max sample size
nn <- length(nseq) # number of sample sizes
# beta-binomial parameters
nbin <- 10 # integers 0, 1,..., 10
# r <- 9 # Wilcox et al. (2014) used 1, 2, 3, and 9
s <- 9 # With r = s = 9 the distribution is bell-shaped and symmetric with mean 5.
# with s=9, r=1, the distribution is heavily positively skewed.
```

# Normal distributions: mean differences

```{r, eval=FALSE}
set.seed(21)
rdist <- rnorm
gpmeans <- c(0, 0.1, 0.2, 0.9)
simres <- sim_apd_mean_diff(rdist, gpmeans) 
save(simres, file = "./data/sim_tp_apd_pval_normal.RData")
fwpr <- apdinter_fwer(simres)
save(fwpr, file = "./data/sim_tp_apd_fwpr_normal.RData")
```

## Results: FWPR
```{r, fig.width=6, fig.height=5}
# default knitr size: {r, fig.width = 7, fig.width = 5}
load(file = "./data/sim_tp_apd_fwpr_normal.RData")
load(file = "./data/sim_tp_apd_pval_normal.RData")
plot.title <- "Normal"
p <- plot_tp_apd_fwpr(fwpr, simres, alpha.val, plot.title)
p
p_fdr_norm <- p
#ggsave(filename = "./figures/fig_tp_apd_fwpr_normal.pdf")
```

Under normality ANOVA on means performs best, followed by ANOVA on trimmed means and finally apd quantile method.

## Results: individual deciles

### Plot by quantile method
```{r, fig.width=8, fig.height=4}
load(file = "./data/sim_tp_apd_pval_normal.RData")
p <- plot_tp_apd_ind(simres, plot.title, alpha.val) 
p
#ggsave(filename = "./figures/fig_tp_apd_ind_normal.pdf")
```

### Plot by sample size
```{r, fig.width=8, fig.height=6}
p <- plot_tp_apd_ind_n(simres, plot.title, alpha.val) 
p
```

Under normality, strongest sensitivity in the middle of the distribution; power decays towards the tails.

# Lognormal distributions: mean differences

```{r, eval=FALSE}
set.seed(21)
rdist <- rlnorm
gpmeans <- c(0, 0, 0, 0.7)
simres <- sim_apd_mean_diff(rdist, gpmeans) 
save(simres, file = "./data/sim_tp_apd_pval_lognormal.RData")
fwpr <- apdinter_fwer(simres)
save(fwpr, file = "./data/sim_tp_apd_fwpr_lognormal.RData")
```

## Results: FWPR
```{r, fig.width=6, fig.height=5}
# default knitr size: {r, fig.width = 7, fig.width = 5}
load(file = "./data/sim_tp_apd_fwpr_lognormal.RData")
load(file = "./data/sim_tp_apd_pval_lognormal.RData")
plot.title <- "Lognormal"
p <- plot_tp_apd_fwpr(fwpr, simres, alpha.val, plot.title)
p
p_fdr_lnorm <- p
#ggsave(filename = "./figures/fig_tp_apd_fwpr_lognormal.pdf")
```

Lognormal distributions: power collapses for the ANOVAs, much more so when making inferences on means vs. trimmed means. Quantile method most powerful for n>40.

## Results: individual deciles

### Plot by quantile method
```{r, fig.width=8, fig.height=4}
load(file = "./data/sim_tp_apd_pval_lognormal.RData")
p <- plot_tp_apd_ind(simres, plot.title, alpha.val) 
p
#ggsave(filename = "./figures/fig_tp_apd_ind_lognormal.pdf")
```

### Plot by sample size
```{r, fig.width=8, fig.height=6}
p <- plot_tp_apd_ind_n(simres, plot.title, alpha.val) 
p
```

Power is very unevenly distributed, with maximum power for the median, dropping non-linearly for lower and upper quantiles.

# Contaminated normal distributions: mean differences

```{r, eval=FALSE}
set.seed(21)
rdist <- cnorm
gpmeans <- c(0, 0.1, 0.2, 0.9)
simres <- sim_apd_mean_diff(rdist, gpmeans) 
save(simres, file = "./data/sim_tp_apd_pval_cnorm.RData")
fwpr <- apdinter_fwer(simres)
save(fwpr, file = "./data/sim_tp_apd_fwpr_cnorm.RData")
```

## Results: FWPR
```{r, fig.width=6, fig.height=5}
# default knitr size: {r, fig.width = 7, fig.width = 5}
load(file = "./data/sim_tp_apd_fwpr_cnorm.RData")
load(file = "./data/sim_tp_apd_pval_cnorm.RData")
plot.title <- "Mixed normal"
p <- plot_tp_apd_fwpr(fwpr, simres, alpha.val, plot.title)
p
p_fdr_cnorm <- p
#ggsave(filename = "./figures/fig_tp_apd_fwpr_cnorm.pdf")
```

Again, very poor performance of the ANOVA on means, but now ANOVA on trimmed means dominates.

## Results: individual deciles

### Plot by quantile method
```{r, fig.width=8, fig.height=4}
load(file = "./data/sim_tp_apd_pval_cnorm.RData")
p <- plot_tp_apd_ind(simres, plot.title, alpha.val) 
p
#ggsave(filename = "./figures/fig_tp_apd_ind_cnorm.pdf")
```

### Plot by sample size
```{r, fig.width=8, fig.height=6}
p <- plot_tp_apd_ind_n(simres, plot.title, alpha.val) 
p
```

# Contaminated lognormal distributions: mean differences

```{r, eval=FALSE}
set.seed(21)
rdist <- clnorm
gpmeans <- c(0, 0, 0, 0.7)
simres <- sim_apd_mean_diff(rdist, gpmeans) 
save(simres, file = "./data/sim_tp_apd_pval_clnorm.RData")
fwpr <- apdinter_fwer(simres)
save(fwpr, file = "./data/sim_tp_apd_fwpr_clnorm.RData")
```

## Results: FWPR
```{r, fig.width=6, fig.height=5}
# default knitr size: {r, fig.width = 7, fig.width = 5}
load(file = "./data/sim_tp_apd_fwpr_clnorm.RData")
load(file = "./data/sim_tp_apd_pval_clnorm.RData")
plot.title <- "Mixed lognormal"
p <- plot_tp_apd_fwpr(fwpr, simres, alpha.val, plot.title)
p
p_fdr_clnorm <- p
#ggsave(filename = "./figures/fig_tp_apd_fwpr_clnorm.pdf")
```

Quantile method most powerful but power is overall low.

## Results: individual deciles

### Plot by quantile method
```{r, fig.width=8, fig.height=4}
load(file = "./data/sim_tp_apd_pval_clnorm.RData")
p <- plot_tp_apd_ind(simres, plot.title, alpha.val) 
p
#ggsave(filename = "./figures/fig_tp_apd_ind_clnorm.pdf")
```

### Plot by sample size
```{r, fig.width=8, fig.height=6}
p <- plot_tp_apd_ind_n(simres, plot.title, alpha.val) 
p
```

# g-and-h distributions: skewness differences

```{r, eval=FALSE}
set.seed(21)
gvals <- c(0, 0, 0, 1)
hvals <- c(0, 0, 0, 0)
simres <- sim_apd_gh_diff(gvals, hvals)
save(simres, file = "./data/sim_tp_apd_pval_gh.RData")
fwpr <- apdinter_fwer(simres)
save(fwpr, file = "./data/sim_tp_apd_fwpr_gh.RData")
```

## Results: FWPR
```{r, fig.width=6, fig.height=5}
# default knitr size: {r, fig.width = 7, fig.width = 5}
load(file = "./data/sim_tp_apd_fwpr_gh.RData")
load(file = "./data/sim_tp_apd_pval_gh.RData")
plot.title <- "g-and-h distributions"
p <- plot_tp_apd_fwpr(fwpr, simres, alpha.val, plot.title)
p
#ggsave(filename = "./figures/fig_tp_apd_fwpr_gh.pdf")
```

ANOVA on means dominates.

## Results: individual deciles

### Plot by quantile method
```{r, fig.width=8, fig.height=4}
load(file = "./data/sim_tp_apd_pval_gh.RData")
p <- plot_tp_apd_ind(simres, plot.title, alpha.val) 
p
#ggsave(filename = "./figures/fig_tp_apd_ind_gh.pdf")
```

### Plot by sample size
```{r, fig.width=8, fig.height=6}
p <- plot_tp_apd_ind_n(simres, plot.title, alpha.val) 
p
```

# g-and-h distributions: skewness differences + outliers

Increase probability of outliers by setting $h=1$.

```{r, eval=FALSE}
set.seed(21)
gvals <- c(0, 0, 0, 1)
hvals <- c(0.1, 0.1, 0.1, 0.1)
simres <- sim_apd_gh_diff(gvals, hvals) 
save(simres, file = "./data/sim_tp_apd_pval_gho.RData")
fwpr <- apdinter_fwer(simres)
save(fwpr, file = "./data/sim_tp_apd_fwpr_gho.RData")
```

## Results: FWPR
```{r, fig.width=6, fig.height=5}
# default knitr size: {r, fig.width = 7, fig.width = 5}
load(file = "./data/sim_tp_apd_fwpr_gho.RData")
load(file = "./data/sim_tp_apd_pval_gho.RData")
plot.title <- "g-and-h distributions + outliers"
p <- plot_tp_apd_fwpr(fwpr, simres, alpha.val, plot.title)
p
#ggsave(filename = "./figures/fig_tp_apd_fwpr_gho.pdf")
```

ANOVA on means dominates.

## Results: individual deciles

### Plot by quantile method
```{r, fig.width=8, fig.height=4}
load(file = "./data/sim_tp_apd_pval_gho.RData")
p <- plot_tp_apd_ind(simres, plot.title, alpha.val) 
p
#ggsave(filename = "./figures/fig_tp_apd_ind_gho.pdf")
```

### Plot by sample size
```{r, fig.width=8, fig.height=6}
p <- plot_tp_apd_ind_n(simres, plot.title, alpha.val) 
p
```

# Beta-binomial distributions

```{r, eval=FALSE}
set.seed(21)
rseq_tp <- c(5.5, 5.5, 5.5, 9)
simres <- apdinter_bb_sim(rseq = rseq_tp, s, nbin, qseq, nseq) 
save(simres, file = "./data/sim_tp_apd_pval_bb.RData")
fwpr <- apdinter_fwer(simres)
save(fwpr, file = "./data/sim_tp_apd_fwpr_bb.RData")
```

## Results: FWPR
```{r, fig.width=6, fig.height=5}
# default knitr size: {r, fig.width = 7, fig.width = 5}
load(file = "./data/sim_tp_apd_fwpr_bb.RData")
load(file = "./data/sim_tp_apd_pval_bb.RData")
plot.title <- "Beta-binomial"
p <- plot_tp_apd_fwpr(fwpr, simres, alpha.val, plot.title)
p
p_fdr_bb <- p
#ggsave(filename = "./figures/fig_tp_apd_fwpr_bb.pdf")
```

ANOVA on means dominates.

## Results: individual deciles

### Plot by quantile method
```{r, fig.width=8, fig.height=4}
load(file = "./data/sim_tp_apd_pval_bb.RData")
p <- plot_tp_apd_ind(simres, plot.title, alpha.val) 
p
#ggsave(filename = "./figures/fig_tp_apd_ind_bb.pdf")
```

### Plot by sample size
```{r, fig.width=8, fig.height=6}
p <- plot_tp_apd_ind_n(simres, plot.title, alpha.val) 
p
```

# Poisson distributions

```{r, eval=FALSE}
set.seed(21)
lambda_tp <- c(7,7,7,9) # Poisson population -- true positives
simres <- apdinter_pois_sim(lambda_tp, qseq) 
save(simres, file = "./data/sim_tp_apd_pval_pois.RData")
fwpr <- decinter_fwer(simres)
save(fwpr, file = "./data/sim_tp_apd_fwpr_pois.RData")
```

## Results: FWPR
```{r, fig.width=6, fig.height=5}
# default knitr size: {r, fig.width = 7, fig.width = 5}
load(file = "./data/sim_tp_apd_fwpr_pois.RData")
load(file = "./data/sim_tp_apd_pval_pois.RData")
plot.title <- "Poisson"
p <- plot_tp_apd_fwpr(fwpr, simres, alpha.val, plot.title)
p
p_fdr_pois <- p
#ggsave(filename = "./figures/fig_tp_apd_fwpr_pois.pdf")
```

ANOVA on means dominates.

## Results: individual deciles

### Plot by quantile method
```{r, fig.width=8, fig.height=4}
load(file = "./data/sim_tp_apd_pval_pois.RData")
p <- plot_tp_apd_ind(simres, plot.title, alpha.val) 
p
#ggsave(filename = "./figures/fig_tp_apd_ind_pois.pdf")
```

### Plot by sample size
```{r, fig.width=8, fig.height=6}
p <- plot_tp_apd_ind_n(simres, plot.title, alpha.val) 
p
```

# Conclusion

No method dominates. In some situations ANOVA on means outperforms the others, yet in other situations, power completely collapses for the ANOVA on means but not for the quantile method.

# Make figures for article

## FWER + FDR

Use all distributions except g-and-h for consistency with other notebooks. So we have 6 sets of results that can fit in a 3 x 2 figure.

```{r, eval=FALSE, warning=FALSE}
legend <- get_legend(p_fdr_norm + guides(color = guide_legend(nrow = 1)) + theme(legend.position = "bottom", legend.box.margin = margin(0, 0, 0, 0)))

pAB <- cowplot::plot_grid(p_fdr_norm + theme(legend.position='none'), 
                          p_fdr_lnorm + theme(legend.position='none'),
                          p_fdr_cnorm + theme(legend.position='none'), 
                          p_fdr_clnorm + theme(legend.position='none'),
                          p_fdr_pois + theme(legend.position='none'), 
                          p_fdr_bb + theme(legend.position='none'),
                          labels=c("A", "B", "C", "D", "E", "F"), 
                          ncol = 2, 
                          nrow = 3,
                          rel_heights = c(1, 1, 1, 1, 1, 1), 
                          label_size = 20, 
                          hjust = -0.5, 
                          scale = 0.95,
                          align = "h")

pAB <- cowplot::plot_grid(pAB, legend,
                          labels=c("", ""), 
                          ncol = 1, 
                          nrow = 2,
                          rel_heights = c(1, 0.05), 
                          label_size = 20, 
                          hjust = -0.5, 
                          scale = 0.95,
                          align = "h") 

pAB

# save figure
ggsave(filename='./figures/fig_art_tp_apd.pdf',width=10,height=12) 
```

