---
title: "Test main effects and interactions at all deciles: false positives"
author: "Rand R. Wilcox & Guillaume A. Rousselet"
date: "`r Sys.Date()`"
output:
  pdf_document:
    fig_caption: no
    number_sections: no
    toc: yes
    toc_depth: 2
    fig_width: 8 
---

Estimate FWER = probability of at least one false negative among 9 deciles.
Use a percentile bootstrap approach as in Wilcox et al. (2014), but with the same samples for all deciles. 
Check whether using separate bootstrap samples for every decile improves coverage in `sim_fp_b1b9.Rmd`.
Compare HD (Harrell & Davis, 1982) to quantile(type=7), the default in R (Hyndman & Fan, 1996; Wicklin, 2017).
Compare two methods to correct for multiple comparisons: Hochberg (1988), as used in Wilcox et al. (2014) and FDR (Benjamini & Hochberg, 1995).
Compare to standard ANOVA on means and 20% trimmed means (no bootstrap, see chapter 7 in Wilcox, 2017).

# Dependencies

```{r, message=FALSE, warning=FALSE}
library(ggplot2)
library(tibble)
library(cowplot)
library(beepr)
source("./code/theme_gar.txt")
source("./code/mainfuns.R")
source("./code/plot.R")
# Compile C++ code:
library(Rcpp)
sourceCpp("./code/decinter_hdqt7.cpp")
```

# Parameters

```{r}
nsim <- 10000 # iterations
nboot <- 2000 # bootstrap samples
inc.step <- 500 # console update every inc.step iterations
qseq <- seq(0.1, 0.9, 0.1)
nq <- length(qseq)
alpha.val <- 0.05
ref.fp <- 1-(1-alpha.val)^nq # FWER for uncorrelated comparisons
nseq <- seq(20, 100, 10) # sample sizes
nmax <- max(nseq) # max sample size
nn <- length(nseq) # number of sample sizes
# Parameters for distributions with tied values
# Poisson parameters
lambda_fp <- c(9,9,9,9) # Poisson population -- false positives
# beta-binomial parameters
nbin <- 10 # integers 0, 1,..., 10
# r <- 9 # Wilcox et al. (2014) used 1, 2, 3, and 9
s <- 9 # With r = s = 9 the distribution is bell-shaped and symmetric with mean 5.
# with s=9, r=1, the distribution is heavily positively skewed.
```

# Normal distributions

```{r, eval=FALSE}
set.seed(21)
rdist <- rnorm
simres <- decinter_fp_sim(rdist)
save(simres, file = "./data/sim_fp_pval_normal.RData")
fwer <- decinter_fwer(simres)
save(fwer, file = "./data/sim_fp_fwer_normal.RData")
```

## Results: FWER
```{r, fig.height=7}
load(file = "./data/sim_fp_pval_normal.RData")
load(file = "./data/sim_fp_fwer_normal.RData")
plot.title <- "Normal"
p <- plot_fp_fwer(fwer, simres, plot.title)
p
#ggsave(filename = "./figures/fig_fp_fwer_normal.pdf", width = 8, height = 10)
```

Horizontal ribbons: dark grey = Bradley's (1978) satisfactory range [0.025; 0.075]; light grey = Bradley's (1978) ideal range [0.045; 0.055]. 

FDR and Hochberg are too conservative, but FDR is closer to nominal level than Hochberg at all sample sizes.

Sanity check: both types of ANOVAs have type I error rates very near 0.05 at all sample sizes. 

HD and QT7 are too conservative, but HD is closer to nominal level than QT7 at all sample sizes, which is easier to appreciate in the next figure.

## Results: FWER - FDR only
```{r, fig.height=7}
p <- plot_fp_fwer_fdr(fwer, simres, plot.title)
p
p_fdr_norm <- p
#ggsave(filename = "./figures/fig_fp_fwer_fdr_normal.pdf", width = 8, height = 10)
```

### FWER for the interaction at n=40

```{r}
todo <- 40
n <- dim(fwer$AB.qt.fdr)[1] # total sample size
qt.res <- binom.test(sum(fwer$AB.qt.fdr[,nseq==todo]), n, p = alpha.val)
hd.res <- binom.test(sum(fwer$AB.hd.fdr[,nseq==todo]), n, p = alpha.val)
```

For the interaction, here is the FWER at n=`r todo` for the two quantile estimators, using FDR correction for multiple comparisons:

- **HD** = `r round(hd.res$estimate, digits=3)` [`r round(hd.res$conf.int[1], digits=3)`, `r round(hd.res$conf.int[2], digits=3)`] 

- **QT7** = `r round(qt.res$estimate, digits=3)` [`r round(qt.res$conf.int[1], digits=3)`, `r round(qt.res$conf.int[2], digits=3)`]

## Results: individual deciles

### Plot by quantile method
```{r, fig.height=7, fig.align='left'}
p <- plot_fp_ind(simres, plot.title, alpha.val)
p
p_ind_norm <- p
#ggsave(filename = "./figures/fig_fp_ind_normal.pdf", width = 8, height = 10)
```

HD and QT7 are too conservative at all quantiles and sample sizes, except for HD at $q_{0.1}$ and $q_{0.9}$, which is too liberal for n=20, and very near 0.05 for n=30. 

### Plot by sample size
```{r, fig.height=10, fig.width=8}
p <- plot_fp_ind_n(simres, plot.title, alpha.val)
p
#ggsave(filename = "./figures/fig_fp_ind_n_normal.pdf", width = 8, height = 10)
```

Except for n=20 for HD, coverage is fairly stable across quantiles and HD dominates QT7.  

# Lognormal distributions: interaction + main effects

```{r, eval=FALSE}
set.seed(21)
rdist <- rlnorm
simres <- decinter_fp_sim(rdist)
save(simres, file = "./data/sim_fp_pval_lognormal.RData")
fwer <- decinter_fwer(simres)
save(fwer, file = "./data/sim_fp_fwer_lognormal.RData")
```

## Results: FWER
```{r, fig.height=7, fig.align='left'}
load(file = "./data/sim_fp_pval_lognormal.RData")
load(file = "./data/sim_fp_fwer_lognormal.RData")
plot.title <- "Lognormal"
p <- plot_fp_fwer(fwer, simres, plot.title)
p
#ggsave(filename = "./figures/fig_fp_fwer_lognormal.pdf", width = 8, height = 10)
```

Similar results to normal: quantile methods are too conservative but better performance is obtained using HD + FDR.  
The two types of ANOVAs are a bit conservative, especially for n=20 and n=30.

## Results: FWER - FDR only
```{r, fig.height=7, fig.align='left'}
p <- plot_fp_fwer_fdr(fwer, simres, plot.title)
p
p_fdr_lnorm <- p
#ggsave(filename = "./figures/fig_fp_fwer_fdr_lognormal.pdf", width = 8, height = 10)
```

### FWER for the interaction at n=40

```{r}
todo <- 40
n <- dim(fwer$AB.qt.fdr)[1] # total sample size
qt.res <- binom.test(sum(fwer$AB.qt.fdr[,nseq==todo]), n, p = alpha.val)
hd.res <- binom.test(sum(fwer$AB.hd.fdr[,nseq==todo]), n, p = alpha.val)
```

For the interaction, here is the FWER at n=`r todo` for the two quantile estimators, using FDR correction for multiple comparisons:

- **HD** = `r round(hd.res$estimate, digits=3)` [`r round(hd.res$conf.int[1], digits=3)`, `r round(hd.res$conf.int[2], digits=3)`] 

- **QT7** = `r round(qt.res$estimate, digits=3)` [`r round(qt.res$conf.int[1], digits=3)`, `r round(qt.res$conf.int[2], digits=3)`]

## Results: individual deciles

### Plot by quantile method
```{r, fig.height=7, fig.align='left'}
p <- plot_fp_ind(simres, plot.title, alpha.val)
p
#ggsave(filename = "./figures/fig_fp_ind_lognormal.pdf", width = 8, height = 10)
```

The last decile $q_{0.9}$ is noisier for HD. HD closer to nominal level than QT7. Stable performance from n=40.

### Plot by sample size
```{r, fig.height=10, fig.width=8}
p <- plot_fp_ind_n(simres, plot.title, alpha.val)
p
#ggsave(filename = "./figures/fig_fp_ind_n_lognormal.pdf", width = 8, height = 10)
```

Both methods are conservative across quantiles, and FWER is lower towards the right tail of the distribution. HD dominates QT7.

# Contaminated normal distributions: interaction + main effects

```{r, eval=FALSE}
set.seed(21)
rdist <- cnorm
simres <- decinter_fp_sim(rdist)
save(simres, file = "./data/sim_fp_pval_cnorm.RData")
fwer <- decinter_fwer(simres)
save(fwer, file = "./data/sim_fp_fwer_cnorm.RData")
```

## Results: FWER
```{r, fig.height=7, fig.align='left'}
load(file = "./data/sim_fp_pval_cnorm.RData")
load(file = "./data/sim_fp_fwer_cnorm.RData")
plot.title <- "Contaminated normal"
p <- plot_fp_fwer(fwer, simres, plot.title)
p
#ggsave(filename = "./figures/fig_fp_fwer_cnorm.pdf", width = 8, height = 10)
```
FDR > Hochberg -- very small differences. 
HD > QT7.

## Results: FWER - FDR only
```{r, fig.height=7, fig.align='left'}
p <- plot_fp_fwer_fdr(fwer, simres, plot.title) + scale_y_continuous(limits = c(0,0.24))
p
#ggsave(filename = "./figures/fig_fp_fwer_fdr_cnorm.pdf", width = 8, height = 10)
```
Again, both estimators lead to conservative inferences except for n=20 and n=30. Strange case in which increasing n leads to worse performance.

### FWER for the interaction at n=40

```{r}
todo <- 40
n <- dim(fwer$AB.qt.fdr)[1] # total sample size
qt.res <- binom.test(sum(fwer$AB.qt.fdr[,nseq==todo]), n, p = alpha.val)
hd.res <- binom.test(sum(fwer$AB.hd.fdr[,nseq==todo]), n, p = alpha.val)
```

For the interaction, here is the FWER at n=`r todo` for the two quantile estimators, using FDR correction for multiple comparisons:

- **HD** = `r round(hd.res$estimate, digits=3)` [`r round(hd.res$conf.int[1], digits=3)`, `r round(hd.res$conf.int[2], digits=3)`] 

- **QT7** = `r round(qt.res$estimate, digits=3)` [`r round(qt.res$conf.int[1], digits=3)`, `r round(qt.res$conf.int[2], digits=3)`]

## Results: individual deciles

### Plot by quantile method
```{r, fig.height=7, fig.align='left'}
p <- plot_fp_ind(simres, plot.title, alpha.val)
p
#ggsave(filename = "./figures/fig_fp_ind_cnorm.pdf", width = 8, height = 10)
```

The behaviour described in the previous chunk is explained here: for n=20, type I error rate is too high for the extreme deciles. We need at least n=40 to make inference about the first and last deciles.

### Plot by sample size
```{r, fig.height=10, fig.width=8}
p <- plot_fp_ind_n(simres, plot.title, alpha.val)
p
#ggsave(filename = "./figures/fig_fp_ind_n_cnorm.pdf", width = 8, height = 10)
```
Coverage deteriorates towards the tails and with lower sample sizes.

# Contaminated lognormal distributions: interaction + main effects

```{r, eval=FALSE}
set.seed(21)
rdist <- clnorm
simres <- decinter_fp_sim(rdist)
save(simres, file = "./data/sim_fp_pval_clnorm.RData")
fwer <- decinter_fwer(simres)
save(fwer, file = "./data/sim_fp_fwer_clnorm.RData")
```

## Results: FWER
```{r, fig.height=7, fig.align='left'}
load(file = "./data/sim_fp_pval_clnorm.RData")
load(file = "./data/sim_fp_fwer_clnorm.RData")
plot.title <- "Contaminated lognormal"
p <- plot_fp_fwer(fwer, simres, plot.title)
p
#ggsave(filename = "./figures/fig_fp_fwer_clnorm.pdf", width = 8, height = 10)
```

FDR > Hochberg, again too conservative.
HD > QT7.

## Results: FWER - FDR only
```{r, fig.height=7, fig.align='left'}
p <- plot_fp_fwer_fdr(fwer, simres, plot.title)
p
#ggsave(filename = "./figures/fig_fp_fwer_fdr_clnorm.pdf", width = 8, height = 10)
```

### FWER for the interaction at n=40

```{r}
todo <- 40
n <- dim(fwer$AB.qt.fdr)[1] # total sample size
qt.res <- binom.test(sum(fwer$AB.qt.fdr[,nseq==todo]), n, p = alpha.val)
hd.res <- binom.test(sum(fwer$AB.hd.fdr[,nseq==todo]), n, p = alpha.val)
```

For the interaction, here is the FWER at n=`r todo` for the two quantile estimators, using FDR correction for multiple comparisons:

- **HD** = `r round(hd.res$estimate, digits=3)` [`r round(hd.res$conf.int[1], digits=3)`, `r round(hd.res$conf.int[2], digits=3)`] 

- **QT7** = `r round(qt.res$estimate, digits=3)` [`r round(qt.res$conf.int[1], digits=3)`, `r round(qt.res$conf.int[2], digits=3)`] 

## Results: individual deciles

### Plot by quantile method
```{r, fig.height=7, fig.align='left'}
p <- plot_fp_ind(simres, plot.title, alpha.val)
p
#ggsave(filename = "./figures/fig_fp_ind_clnorm.pdf", width = 8, height = 10)
```

### Plot by sample size
```{r, fig.height=10, fig.width=8}
p <- plot_fp_ind_n(simres, plot.title, alpha.val)
p
#ggsave(filename = "./figures/fig_fp_ind_n_clnorm.pdf", width = 8, height = 10)
```

Coverage deteriorates towards right tail and with lower sample sizes.

# Poisson distributions

```{r, eval=FALSE}
set.seed(21)
rdist <- rnorm
simres <- decinter_pois_sim(lambda_fp, qseq)
save(simres, file = "./data/sim_fp_pval_pois.RData")
fwer <- decinter_fwer(simres)
save(fwer, file = "./data/sim_fp_fwer_pois.RData")
```

## Results: FWER
```{r, fig.height=7, fig.align='left'}
load(file = "./data/sim_fp_pval_pois.RData")
load(file = "./data/sim_fp_fwer_pois.RData")
plot.title <- "Poisson"
p <- plot_fp_fwer(fwer, simres, plot.title)
p
#ggsave(filename = "./figures/fig_fp_fwer_pois.pdf", width = 8, height = 10)
```

FDR > Hochberg, closer to nominal level but overall conservative. 
HD > QT7.
ANOVAs perform well.

## Results: FWER - FDR only
```{r, fig.height=7, fig.align='left'}
p <- plot_fp_fwer_fdr(fwer, simres, plot.title)
p
p_fdr_pois <- p
#ggsave(filename = "./figures/fig_fp_fwer_fdr_pois.pdf", width = 8, height = 10)
```

HD dominates QT7.

### FWER for the interaction at n=40

```{r}
todo <- 40
n <- dim(fwer$AB.qt.fdr)[1] # total sample size
qt.res <- binom.test(sum(fwer$AB.qt.fdr[,nseq==todo]), n, p = alpha.val)
hd.res <- binom.test(sum(fwer$AB.hd.fdr[,nseq==todo]), n, p = alpha.val)
```

For the interaction, here is the FWER at n=`r todo` for the two quantile estimators, using FDR correction for multiple comparisons:

- **HD** = `r round(hd.res$estimate, digits=3)` [`r round(hd.res$conf.int[1], digits=3)`, `r round(hd.res$conf.int[2], digits=3)`] 

- **QT7** = `r round(qt.res$estimate, digits=3)` [`r round(qt.res$conf.int[1], digits=3)`, `r round(qt.res$conf.int[2], digits=3)`]

## Results: individual deciles

### Plot by quantile method
```{r, fig.height=7, fig.align='left'}
p <- plot_fp_ind(simres, plot.title, alpha.val)
p
#ggsave(filename = "./figures/fig_fp_ind_pois.pdf", width = 8, height = 10)
```

### Plot by sample size
```{r, fig.height=10, fig.width=8}
p <- plot_fp_ind_n(simres, plot.title, alpha.val)
p
#ggsave(filename = "./figures/fig_fp_ind_n_pois.pdf", width = 8, height = 10)
```

# Beta-binomial distributions: r=1

```{r, eval=FALSE}
set.seed(21)
rseq_fp <- c(1,1,1,1)
simres <- decinter_bb_sim(rseq=rseq_fp, s=s, nbin=nbin, qseq, nseq)
save(simres, file = "./data/sim_fp_pval_bbr1.RData")
fwer <- decinter_fwer(simres)
save(fwer, file = "./data/sim_fp_fwer_bbr1.RData")
```

## Results: FWER
```{r, fig.height=7, fig.align='left'}
load(file = "./data/sim_fp_pval_bbr1.RData")
load(file = "./data/sim_fp_fwer_bbr1.RData")
plot.title <- "Beta-binomial (r=1)"
p <- plot_fp_fwer(fwer, simres, plot.title)
p
#ggsave(filename = "./figures/fig_fp_fwer_bbr1.pdf", width = 8, height = 10)
```

FDR > Hochberg, closer to nominal level but overall conservative. 
HD performs much better than QT7.

## Results: FWER - FDR only
```{r, fig.height=7, fig.align='left'}
p <- plot_fp_fwer_fdr(fwer, simres, plot.title)
p
#ggsave(filename = "./figures/fig_fp_fwer_fdr_bbr1.pdf", width = 8, height = 10)
```

### FWER for the interaction at n=40

```{r}
todo <- 40
n <- dim(fwer$AB.qt.fdr)[1] # total sample size
qt.res <- binom.test(sum(fwer$AB.qt.fdr[,nseq==todo]), n, p = alpha.val)
hd.res <- binom.test(sum(fwer$AB.hd.fdr[,nseq==todo]), n, p = alpha.val)
```

For the interaction, here is the FWER at n=`r todo` for the two quantile estimators, using FDR correction for multiple comparisons:

- **HD** = `r round(hd.res$estimate, digits=3)` [`r round(hd.res$conf.int[1], digits=3)`, `r round(hd.res$conf.int[2], digits=3)`] 

- **QT7** = `r round(qt.res$estimate, digits=3)` [`r round(qt.res$conf.int[1], digits=3)`, `r round(qt.res$conf.int[2], digits=3)`]

## Results: individual deciles

### Plot by quantile method
```{r, fig.height=7, fig.align='left'}
p <- plot_fp_ind(simres, plot.title, alpha.val)
p
#ggsave(filename = "./figures/fig_fp_ind_bbr1.pdf", width = 8, height = 10)
```

### Plot by sample size
```{r, fig.height=10, fig.width=8}
p <- plot_fp_ind_n(simres, plot.title, alpha.val)
p
#ggsave(filename = "./figures/fig_fp_ind_n_bbr1.pdf", width = 8, height = 10)
```

# Beta-binomial distributions: r=9

```{r, eval=FALSE}
set.seed(21)
rseq_fp <- c(9,9,9,9)
simres <- decinter_bb_sim(rseq=rseq_fp, s=s, nbin=nbin, qseq, nseq)
save(simres, file = "./data/sim_fp_pval_bbr9.RData")
fwer <- decinter_fwer(simres)
save(fwer, file = "./data/sim_fp_fwer_bbr9.RData")
```

## Results: FWER
```{r, fig.height=7, fig.align='left'}
load(file = "./data/sim_fp_pval_bbr9.RData")
load(file = "./data/sim_fp_fwer_bbr9.RData")
plot.title <- "Beta-binomial (r=9)"
p <- plot_fp_fwer(fwer, simres, plot.title)
p
#ggsave(filename = "./figures/fig_fp_fwer_bbr9.pdf", width = 8, height = 10)
```

FDR a bit better than Hochberg, closer to nominal level but overall conservative.
HD performs much better than QT7.  

## Results: FWER - FDR only
```{r, fig.height=7, fig.align='left'}
p <- plot_fp_fwer_fdr(fwer, simres, plot.title)
p
p_fdr_bbr9 <- p
#ggsave(filename = "./figures/fig_fp_fwer_fdr_bbr9.pdf", width = 8, height = 10)
```

### FWER for the interaction at n=40

```{r}
todo <- 40
n <- dim(fwer$AB.qt.fdr)[1] # total sample size
qt.res <- binom.test(sum(fwer$AB.qt.fdr[,nseq==todo]), n, p = alpha.val)
hd.res <- binom.test(sum(fwer$AB.hd.fdr[,nseq==todo]), n, p = alpha.val)
```

For the interaction, here is the FWER at n=`r todo` for the two quantile estimators, using FDR correction for multiple comparisons:

- **HD** = `r round(hd.res$estimate, digits=3)` [`r round(hd.res$conf.int[1], digits=3)`, `r round(hd.res$conf.int[2], digits=3)`] 

- **QT7** = `r round(qt.res$estimate, digits=3)` [`r round(qt.res$conf.int[1], digits=3)`, `r round(qt.res$conf.int[2], digits=3)`]

## Results: individual deciles

### Plot by quantile method
```{r, fig.height=7, fig.align='left'}
p <- plot_fp_ind(simres, plot.title, alpha.val)
p
p_ind_bbr9 <- p
#ggsave(filename = "./figures/fig_fp_ind_bbr9.pdf", width = 8, height = 10)
```

### Plot by sample size
```{r, fig.height=10, fig.width=8}
p <- plot_fp_ind_n(simres, plot.title, alpha.val)
p
#ggsave(filename = "./figures/fig_fp_ind_n_bbr9.pdf", width = 8, height = 10)
```

# Conclusion

All methods tested are a bit too conservative. FDR gives FWER closer to nominal level than Hochberg across all conditions. FDR dominates QT7 in all situations. 
Recommendation: use HD + FDR as default.

# Make figures for article

## FWER + FDR: normal + lognormal
```{r, eval=FALSE, warning=FALSE}
legend <- get_legend(p_fdr_norm + guides(color = guide_legend(nrow = 1)) + theme(legend.position = "bottom", legend.box.margin = margin(0, 0, 0, 0)))

pAB <- cowplot::plot_grid(p_fdr_norm + theme(legend.position='none'), 
                          p_fdr_lnorm + theme(legend.position='none'),
                          labels=c("A", "B"), 
                          ncol = 2, 
                          nrow = 1,
                          rel_heights = c(1, 1), 
                          label_size = 20, 
                          hjust = -0.5, 
                          scale = 0.95,
                          align = "h")

pAB <- cowplot::plot_grid(pAB, legend,
                          labels=c("", ""), 
                          ncol = 1, 
                          nrow = 2,
                          rel_heights = c(1, 0.05), 
                          label_size = 20, 
                          hjust = -0.5, 
                          scale = 0.95,
                          align = "h") 

pAB

# save figure
ggsave(filename='./figures/fig_art_fp_norm_lnorm.pdf',width=12,height=8) 
```

## FWER + FDR: Poisson + beta-binomial (r=9)
```{r, eval=FALSE, warning=FALSE}
legend <- get_legend(p_fdr_norm + guides(color = guide_legend(nrow = 1)) + theme(legend.position = "bottom", legend.box.margin = margin(0, 0, 0, 0)))

pAB <- cowplot::plot_grid(p_fdr_pois + theme(legend.position='none'), 
                          p_fdr_bbr9 + theme(legend.position='none'),
                          labels=c("A", "B"), 
                          ncol = 2, 
                          nrow = 1,
                          rel_heights = c(1, 1), 
                          label_size = 20, 
                          hjust = -0.5, 
                          scale = 0.95,
                          align = "h")

pAB <- cowplot::plot_grid(pAB, legend,
                          labels=c("", ""), 
                          ncol = 1, 
                          nrow = 2,
                          rel_heights = c(1, 0.05), 
                          label_size = 20, 
                          hjust = -0.5, 
                          scale = 0.95,
                          align = "h") 

pAB

# save figure
ggsave(filename='./figures/fig_art_fp_pois_bbr9.pdf',width=12,height=8) 
```

## Results at individual deciles: normal + beta-binomial (r=9)
```{r, eval=FALSE, warning=FALSE}
# legend <- get_legend(p_ind_norm)
legend <- get_legend(p_ind_norm + guides(color = guide_legend(nrow = 3)) + theme(legend.position = "bottom", legend.box.margin = margin(0, 0, 0, 0)))

cowplot::plot_grid(p_ind_norm + theme(legend.position='none'), 
                   p_ind_bbr9 + theme(legend.position='none'),
                   legend,
                   NULL,
                   labels=c("A", "B", "",  ""), 
                   ncol = 2, 
                   nrow = 2,
                   rel_widths = c(1, 1), 
                   rel_heights = c(1, 0.2),
                   label_size = 20, 
                   hjust = -0.5, 
                   scale = 1,
                   align = "h")

# save figure
ggsave(filename='./figures/fig_art_fp_ind_norm_bbr9.pdf',width=15,height=10) 
```


# References

Benjamini, Y. & Hochberg, Y. (1995) Controlling the False Discovery Rate: A Practical and Powerful Approach to Multiple Testing. Journal of the Royal Statistical Society: Series B (Methodological), 57, 289–300.

Bradley, J.V. (1978) Robustness? British Journal of Mathematical and Statistical Psychology, 31, 144–152.

Harrell, F.E. & Davis, C.E. (1982) A new distribution-free quantile estimator. Biometrika, 69, 635–640.

Hochberg, Y. (1988) A sharper Bonferroni procedure for multiple tests of significance. Biometrika, 75, 800–802.

Hyndman, R.J. & Fan, Y. (1996) Sample Quantiles in Statistical Packages. The American Statistician, 50, 361.

Wicklin, R. (2017) Sample quantiles: A comparison of 9 definitions; SAS Blog. https://blogs.sas.com/content/iml/2017/05/24/definitions-sample-quantiles.html

Wilcox, R.R. (2017) Introduction to Robust Estimation and Hypothesis Testing, 4th edition. edn. Academic Press.

Wilcox, R.R., Erceg-Hurn, D.M., Clark, F., & Carlson, M. (2014) Comparing two independent groups via the lower and upper quantiles. Journal of Statistical Computation and Simulation, 84, 1543–1551.

