---
title: "Test main effects and interactions: false positives, boot1 vs. boot9"
author: "Rand R. Wilcox & Guillaume A. Rousselet"
date: "`r Sys.Date()`"
output:
  pdf_document:
    fig_caption: no
    number_sections: no
    toc: yes
    toc_depth: 2
    fig_width: 8 
---

Estimate FWER = probability of at least one false negative among 9 deciles.
Use HD only; compare bootstrap with the same samples for all deciles vs. different samples. 

# Dependencies

```{r, message=FALSE, warning=FALSE}
library(ggplot2)
library(tibble)
library(beepr)
source("./code/theme_gar.txt")
source("./code/mainfuns.R")
source("./code/plot.R")
# Compile C++ code:
library(Rcpp)
sourceCpp("./code/decinter_b1b9.cpp")
```

# Parameters

```{r}
nsim <- 10000 # iterations
nboot <- 2000 # bootstrap samples
inc.step <- 500 # beep every inc.step iterations
qseq <- seq(0.1, 0.9, 0.1)
nq <- length(qseq)
alpha.val <- 0.05
ref.fp <- 1-(1-alpha.val)^nq # FWER for uncorrelated comparisons
nseq <- seq(20, 100, 10) # sample sizes
nmax <- max(nseq) # max sample size
nn <- length(nseq) # number of sample sizes
```

# Normal distributions: interaction + main effects

```{r, eval=FALSE}
set.seed(21)
rdist <- rnorm
simres <- decinter_b1b9_sim(rdist)
save(simres, file = "./data/sim_fp_pval_normal_b1b9.RData")
fwer <- decinter_b1b9_fwer(simres)
save(fwer, file = "./data/sim_fp_fwer_normal_b1b9.RData")
```

## Results: FWER
```{r}
load(file = "./data/sim_fp_fwer_normal_b1b9.RData")
plot.title <- "Normal"
p <- plot_fp_fwer_fdr_b1b9(fwer, plot.title)
p
#ggsave(filename = "./figures/fig_fp_fwer_fdr_normal_b1b9.pdf", width = 8, height = 10)
```

# Lognormal distributions: interaction + main effects

```{r, eval=FALSE}
set.seed(21)
rdist <- rlnorm
simres <- decinter_b1b9_sim(rdist)
save(simres, file = "./data/sim_fp_pval_lognormal_b1b9.RData")
fwer <- decinter_b1b9_fwer(simres)
save(fwer, file = "./data/sim_fp_fwer_lognormal_b1b9.RData")
```

## Results: FWER
```{r}
load(file = "./data/sim_fp_fwer_lognormal_b1b9.RData")
plot.title <- "Lognormal"
p <- plot_fp_fwer_fdr_b1b9(fwer, plot.title)
p
#ggsave(filename = "./figures/fig_fp_fwer_fdr_lognormal_b1b9.pdf", width = 8, height = 10)
```

# Contaminated normal distributions: interaction + main effects

```{r, eval=FALSE}
set.seed(21)
rdist <- cnorm
simres <- decinter_b1b9_sim(rdist)
save(simres, file = "./data/sim_fp_pval_cnorm_b1b9.RData")
fwer <- decinter_b1b9_fwer(simres)
save(fwer, file = "./data/sim_fp_fwer_cnorm_b1b9.RData")
```

## Results: FWER
```{r}
load(file = "./data/sim_fp_fwer_cnorm_b1b9.RData")
plot.title <- "Contaminated normal"
p <- plot_fp_fwer_fdr_b1b9(fwer, plot.title)
p
#ggsave(filename = "./figures/fig_fp_fwer_fdr_cnorm_b1b9.pdf", width = 8, height = 10)
```

# Contaminated lognormal distributions: interaction + main effects

```{r, eval=FALSE}
set.seed(21)
rdist <- clnorm
simres <- decinter_b1b9_sim(rdist)
save(simres, file = "./data/sim_fp_pval_clnorm_b1b9.RData")
fwer <- decinter_b1b9_fwer(simres)
save(fwer, file = "./data/sim_fp_fwer_clnorm_b1b9.RData")
```

## Results: FWER
```{r}
load(file = "./data/sim_fp_fwer_clnorm_b1b9.RData")
plot.title <- "Contaminated lognormal"
p <- plot_fp_fwer_fdr_b1b9(fwer, plot.title)
p
#ggsave(filename = "./figures/fig_fp_fwer_fdr_clnorm_b1b9.pdf", width = 8, height = 10)
```

# Conclusion
No evidence for better performance using separate bootstrap samples for every decile.
Keep using the same bootstrap samples for all deciles for computational efficiency.
Overall the approach is conservative, with FWER below the nominal level at all sample sizes, for all distributions, and for main effects and interaction.

