---
title: "Quantile differences between distributions of all pairwise differences: false positives"
author: "Rand R. Wilcox & Guillaume A. Rousselet"
date: "`r Sys.Date()`"
output:
  pdf_document:
    fig_caption: no
    number_sections: no
    toc: yes
    toc_depth: 2
    fig_width: 8 
---

Strategy: for each level of A, compute all pairwise differences between B1 and B2. Then compare the quantiles (here deciles) of these two distributions. 

Estimate FWER = probability of at least one false negative among 9 deciles.
Use percentile bootstrap only and boot1 method = use the same bootstrap samples for all deciles. 

# Dependencies

```{r, message=FALSE, warning=FALSE}
library(ggplot2)
library(tibble)
library(beepr)
library(cowplot)
source("./code/theme_gar.txt")
source("./code/mainfuns.R")
source("./code/plot.R")
# Compile C++ code:
library(Rcpp)
sourceCpp("./code/apdinter_hdqt7.cpp")
```

# Parameters

```{r}
nsim <- 10000 # iterations
nboot <- 2000 # bootstrap samples
inc.step <- 500 # beep every inc.step iterations
qseq <- seq(0.1, 0.9, 0.1)
nq <- length(qseq)
alpha.val <- 0.05
ref.fp <- 1-(1-alpha.val)^nq # FWER for uncorrelated comparisons
nseq <- seq(20, 100, 10) # sample sizes
nmax <- max(nseq) # max sample size
nn <- length(nseq) # number of sample sizes
# Parameters for distributions with tied values
# beta-binomial parameters
nbin <- 10 # integers 0, 1,..., 10
# r <- 9 # Wilcox et al. (2014) used 1, 2, 3, and 9
s <- 9 # With r = s = 9 the distribution is bell-shaped and symmetric with mean 5.
# with s=9, r=1, the distribution is heavily positively skewed.
```

# Normal distributions

```{r, eval=FALSE}
set.seed(21)
rdist <- rnorm
simres <- apdinter_sim(rdist)
save(simres, file = "./data/sim_fp_apd_pval_normal.RData")
fwer <- apdinter_fwer(simres)
save(fwer, file = "./data/sim_fp_apd_fwer_normal.RData")
```

## Results: FWER
```{r}
load(file = "./data/sim_fp_apd_fwer_normal.RData")
plot.title <- "Normal"
p <- plot_fp_apd_fwer(fwer, plot.title) 
p
#ggsave(filename = "./figures/fig_fp_apd_fwer_fdr_normal.pdf", width = 8, height = 10)
```

## Results: FWER - FDR only
```{r}
p <- plot_fp_apd_fwer_fdr(fwer, plot.title) 
p
p_fdr_norm <- p
```

### FWER for the interaction at n=40

```{r}
todo <- 40
n <- dim(fwer$AB.qt.fdr)[1] # total sample size
qt.res <- binom.test(sum(fwer$AB.qt.fdr[,nseq==todo]), n, p = alpha.val)
hd.res <- binom.test(sum(fwer$AB.hd.fdr[,nseq==todo]), n, p = alpha.val)
```

For the interaction, here is the FWER at n=`r todo` for the two quantile estimators, using FDR correction for multiple comparisons:

- **HD** = `r round(hd.res$estimate, digits=3)` [`r round(hd.res$conf.int[1], digits=3)`, `r round(hd.res$conf.int[2], digits=3)`] 

- **QT7** = `r round(qt.res$estimate, digits=3)` [`r round(qt.res$conf.int[1], digits=3)`, `r round(qt.res$conf.int[2], digits=3)`]

## Results: individual deciles

### Plot by quantile method
```{r, fig.height=4, fig.width=8}
load(file = "./data/sim_fp_apd_pval_normal.RData")
p <- plot_fp_apd_ind(simres, plot.title, alpha.val)
p 
p_ind_norm <- p
#ggsave(filename = "./figures/fig_fp_apd_ind_normal.pdf", width = 8, height = 4)
```

### Plot by sample size
```{r, fig.height=8, fig.width=8}
p <- plot_fp_apd_ind_n(simres, plot.title, alpha.val)
p
#ggsave(filename = "./figures/fig_fp_ind_n_normal.pdf", width = 8, height = 8)
```

# Lognormal distributions

```{r, eval=FALSE}
set.seed(21)
rdist <- rlnorm
simres <- apdinter_sim(rdist)
save(simres, file = "./data/sim_fp_apd_pval_lognormal.RData")
fwer <- apdinter_fwer(simres)
save(fwer, file = "./data/sim_fp_apd_fwer_lognormal.RData")
```

## Results: FWER
```{r}
load(file = "./data/sim_fp_apd_fwer_lognormal.RData")
plot.title <- "Lognormal"
p <- plot_fp_apd_fwer(fwer, plot.title)
p
#ggsave(filename = "./figures/fig_fp_apd_fwer_fdr_lognormal.pdf", width = 8, height = 10)
```

## Results: FWER - FDR only
```{r}
p <- plot_fp_apd_fwer_fdr(fwer, plot.title) 
p
p_fdr_lnorm <- p
```

### FWER for the interaction at n=40

```{r}
todo <- 40
n <- dim(fwer$AB.qt.fdr)[1] # total sample size
qt.res <- binom.test(sum(fwer$AB.qt.fdr[,nseq==todo]), n, p = alpha.val)
hd.res <- binom.test(sum(fwer$AB.hd.fdr[,nseq==todo]), n, p = alpha.val)
```

For the interaction, here is the FWER at n=`r todo` for the two quantile estimators, using FDR correction for multiple comparisons:

- **HD** = `r round(hd.res$estimate, digits=3)` [`r round(hd.res$conf.int[1], digits=3)`, `r round(hd.res$conf.int[2], digits=3)`] 

- **QT7** = `r round(qt.res$estimate, digits=3)` [`r round(qt.res$conf.int[1], digits=3)`, `r round(qt.res$conf.int[2], digits=3)`]

## Results: individual deciles

### Plot by quantile method
```{r, fig.height=4, fig.width=8}
load(file = "./data/sim_fp_apd_pval_lognormal.RData")
p <- plot_fp_apd_ind(simres, plot.title, alpha.val)
p
#ggsave(filename = "./figures/fig_fp_apd_ind_lognormal.pdf", width = 8, height = 4)
```

### Plot by sample size
```{r, fig.height=8, fig.width=8}
p <- plot_fp_apd_ind_n(simres, plot.title, alpha.val)
p
#ggsave(filename = "./figures/fig_fp_ind_n_lognormal.pdf", width = 8, height = 8)
```

# Contaminated normal distributions

Called mixed distributions in the article.

```{r, eval=FALSE}
set.seed(21)
rdist <- cnorm
simres <- apdinter_sim(rdist)
save(simres, file = "./data/sim_fp_apd_pval_cnorm.RData")
fwer <- apdinter_fwer(simres)
save(fwer, file = "./data/sim_fp_apd_fwer_cnorm.RData")
```

## Results: FWER
```{r}
load(file = "./data/sim_fp_apd_fwer_cnorm.RData")
plot.title <- "Mixed normal"
p <- plot_fp_apd_fwer(fwer, plot.title)
p
#ggsave(filename = "./figures/fig_fp_apd_fwer_fdr_cnorm.pdf", width = 8, height = 10)
```

## Results: FWER - FDR only
```{r}
p <- plot_fp_apd_fwer_fdr(fwer, plot.title) 
p
p_fdr_cnorm <- p
```

### FWER for the interaction at n=40

```{r}
todo <- 40
n <- dim(fwer$AB.qt.fdr)[1] # total sample size
qt.res <- binom.test(sum(fwer$AB.qt.fdr[,nseq==todo]), n, p = alpha.val)
hd.res <- binom.test(sum(fwer$AB.hd.fdr[,nseq==todo]), n, p = alpha.val)
```

For the interaction, here is the FWER at n=`r todo` for the two quantile estimators, using FDR correction for multiple comparisons:

- **HD** = `r round(hd.res$estimate, digits=3)` [`r round(hd.res$conf.int[1], digits=3)`, `r round(hd.res$conf.int[2], digits=3)`] 

- **QT7** = `r round(qt.res$estimate, digits=3)` [`r round(qt.res$conf.int[1], digits=3)`, `r round(qt.res$conf.int[2], digits=3)`]

## Results: individual deciles

### Plot by quantile method
```{r, fig.height=4, fig.width=8}
load(file = "./data/sim_fp_apd_pval_cnorm.RData")
p <- plot_fp_apd_ind(simres, plot.title, alpha.val)
p
#ggsave(filename = "./figures/fig_fp_apd_ind_cnorm.pdf", width = 8, height = 4)
```

### Plot by sample size
```{r, fig.height=8, fig.width=8}
p <- plot_fp_apd_ind_n(simres, plot.title, alpha.val)
p
#ggsave(filename = "./figures/fig_fp_ind_n_cnorm.pdf", width = 8, height = 8)
```

# Contaminated lognormal distributions

```{r, eval=FALSE}
set.seed(21)
rdist <- clnorm
simres <- apdinter_sim(rdist)
save(simres, file = "./data/sim_fp_apd_pval_clnorm.RData")
fwer <- apdinter_fwer(simres)
save(fwer, file = "./data/sim_fp_apd_fwer_clnorm.RData")
```

## Results: FWER
```{r}
load(file = "./data/sim_fp_apd_fwer_clnorm.RData")
plot.title <- "Mixed lognormal"
p <- plot_fp_apd_fwer(fwer, plot.title)
p
#ggsave(filename = "./figures/fig_fp_apd_fwer_fdr_clnorm.pdf", width = 8, height = 10)
```

## Results: FWER - FDR only
```{r}
p <- plot_fp_apd_fwer_fdr(fwer, plot.title) 
p
p_fdr_clnorm <- p
```

### FWER for the interaction at n=40

```{r}
todo <- 40
n <- dim(fwer$AB.qt.fdr)[1] # total sample size
qt.res <- binom.test(sum(fwer$AB.qt.fdr[,nseq==todo]), n, p = alpha.val)
hd.res <- binom.test(sum(fwer$AB.hd.fdr[,nseq==todo]), n, p = alpha.val)
```

For the interaction, here is the FWER at n=`r todo` for the two quantile estimators, using FDR correction for multiple comparisons:

- **HD** = `r round(hd.res$estimate, digits=3)` [`r round(hd.res$conf.int[1], digits=3)`, `r round(hd.res$conf.int[2], digits=3)`] 

- **QT7** = `r round(qt.res$estimate, digits=3)` [`r round(qt.res$conf.int[1], digits=3)`, `r round(qt.res$conf.int[2], digits=3)`]

## Results: individual deciles

### Plot by quantile method
```{r, fig.height=4, fig.width=8}
load(file = "./data/sim_fp_apd_pval_clnorm.RData")
p <- plot_fp_apd_ind(simres, plot.title, alpha.val)
p
p_ind_clnorm <- p
#ggsave(filename = "./figures/fig_fp_apd_ind_clnorm.pdf", width = 8, height = 4)
```

### Plot by sample size
```{r, fig.height=8, fig.width=8}
p <- plot_fp_apd_ind_n(simres, plot.title, alpha.val)
p
#ggsave(filename = "./figures/fig_fp_ind_n_clnorm.pdf", width = 8, height = 8)
```

# Poisson distributions

```{r, eval=FALSE}
set.seed(21)
lambda_fp <- c(9,9,9,9) # Poisson population -- false positives
simres <- apdinter_pois_sim(lambda_fp, qseq)
save(simres, file = "./data/sim_fp_apd_pval_pois.RData")
fwer <- apdinter_fwer(simres)
save(fwer, file = "./data/sim_fp_apd_fwer_pois.RData")
```

## Results: FWER
```{r}
load(file = "./data/sim_fp_apd_fwer_pois.RData")
plot.title <- "Poisson"
p <- plot_fp_apd_fwer(fwer, plot.title)
p
#ggsave(filename = "./figures/fig_fp_apd_fwer_fdr_pois.pdf", width = 8, height = 10)
```

## Results: FWER - FDR only
```{r}
p <- plot_fp_apd_fwer_fdr(fwer, plot.title) 
p
p_fdr_pois <- p
```

### FWER for the interaction at n=40

```{r}
todo <- 40
n <- dim(fwer$AB.qt.fdr)[1] # total sample size
qt.res <- binom.test(sum(fwer$AB.qt.fdr[,nseq==todo]), n, p = alpha.val)
hd.res <- binom.test(sum(fwer$AB.hd.fdr[,nseq==todo]), n, p = alpha.val)
```

For the interaction, here is the FWER at n=`r todo` for the two quantile estimators, using FDR correction for multiple comparisons:

- **HD** = `r round(hd.res$estimate, digits=3)` [`r round(hd.res$conf.int[1], digits=3)`, `r round(hd.res$conf.int[2], digits=3)`] 

- **QT7** = `r round(qt.res$estimate, digits=3)` [`r round(qt.res$conf.int[1], digits=3)`, `r round(qt.res$conf.int[2], digits=3)`]

## Results: individual deciles

### Plot by quantile method
```{r, fig.height=4, fig.width=8}
load(file = "./data/sim_fp_apd_pval_pois.RData")
p <- plot_fp_apd_ind(simres, plot.title, alpha.val)
p
p_ind_pois <- p
#ggsave(filename = "./figures/fig_fp_apd_ind_pois.pdf", width = 8, height = 4)
```

### Plot by sample size
```{r, fig.height=8, fig.width=8}
p <- plot_fp_apd_ind_n(simres, plot.title, alpha.val)
p
#ggsave(filename = "./figures/fig_fp_ind_n_pois.pdf", width = 8, height = 8)
```

# Beta-binomial distributions: r=1

```{r, eval=FALSE}
set.seed(21)
rseq_fp <- c(1,1,1,1)
simres <- apdinter_bb_sim(rseq=rseq_fp, s=s, nbin=nbin, qseq, nseq)
save(simres, file = "./data/sim_fp_apd_pval_bbr1.RData")
fwer <- apdinter_fwer(simres)
save(fwer, file = "./data/sim_fp_apd_fwer_bbr1.RData")
```

## Results: FWER
```{r}
load(file = "./data/sim_fp_apd_fwer_bbr1.RData")
plot.title <- "Beta-binomial (r=1)"
p <- plot_fp_apd_fwer(fwer, plot.title)
p
#ggsave(filename = "./figures/fig_fp_apd_fwer_fdr_bbr1.pdf", width = 8, height = 10)
```

## Results: FWER - FDR only
```{r}
p <- plot_fp_apd_fwer_fdr(fwer, plot.title) 
p
```

### FWER for the interaction at n=40

```{r}
todo <- 40
n <- dim(fwer$AB.qt.fdr)[1] # total sample size
qt.res <- binom.test(sum(fwer$AB.qt.fdr[,nseq==todo]), n, p = alpha.val)
hd.res <- binom.test(sum(fwer$AB.hd.fdr[,nseq==todo]), n, p = alpha.val)
```

For the interaction, here is the FWER at n=`r todo` for the two quantile estimators, using FDR correction for multiple comparisons:

- **HD** = `r round(hd.res$estimate, digits=3)` [`r round(hd.res$conf.int[1], digits=3)`, `r round(hd.res$conf.int[2], digits=3)`] 

- **QT7** = `r round(qt.res$estimate, digits=3)` [`r round(qt.res$conf.int[1], digits=3)`, `r round(qt.res$conf.int[2], digits=3)`]

## Results: individual deciles

### Plot by quantile method
```{r, fig.height=4, fig.width=8}
load(file = "./data/sim_fp_apd_pval_bbr1.RData")
p <- plot_fp_apd_ind(simres, plot.title, alpha.val)
p
p_ind_bbr1 <- p
#ggsave(filename = "./figures/fig_fp_apd_ind_bbr1.pdf", width = 8, height = 4)
```

### Plot by sample size
```{r, fig.height=8, fig.width=8}
p <- plot_fp_apd_ind_n(simres, plot.title, alpha.val)
p
#ggsave(filename = "./figures/fig_fp_ind_n_bbr1.pdf", width = 8, height = 8)
```

# Beta-binomial distributions: r=9

```{r, eval=FALSE}
set.seed(21)
rseq_fp <- c(9,9,9,9)
simres <- apdinter_bb_sim(rseq=rseq_fp, s=s, nbin=nbin, qseq, nseq)
save(simres, file = "./data/sim_fp_apd_pval_bbr9.RData")
fwer <- apdinter_fwer(simres)
save(fwer, file = "./data/sim_fp_apd_fwer_bbr9.RData")
```

## Results: FWER
```{r}
load(file = "./data/sim_fp_apd_fwer_bbr9.RData")
plot.title <- "Beta-binomial (r=9)"
p <- plot_fp_apd_fwer(fwer, plot.title)
p
#ggsave(filename = "./figures/fig_fp_apd_fwer_fdr_bbr9.pdf", width = 8, height = 10)
```

## Results: FWER - FDR only
```{r}
p <- plot_fp_apd_fwer_fdr(fwer, plot.title) 
p
p_fdr_bbr9 <- p
```

### FWER for the interaction at n=40

```{r}
todo <- 40
n <- dim(fwer$AB.qt.fdr)[1] # total sample size
qt.res <- binom.test(sum(fwer$AB.qt.fdr[,nseq==todo]), n, p = alpha.val)
hd.res <- binom.test(sum(fwer$AB.hd.fdr[,nseq==todo]), n, p = alpha.val)
```

For the interaction, here is the FWER at n=`r todo` for the two quantile estimators, using FDR correction for multiple comparisons:

- **HD** = `r round(hd.res$estimate, digits=3)` [`r round(hd.res$conf.int[1], digits=3)`, `r round(hd.res$conf.int[2], digits=3)`] 

- **QT7** = `r round(qt.res$estimate, digits=3)` [`r round(qt.res$conf.int[1], digits=3)`, `r round(qt.res$conf.int[2], digits=3)`]

## Results: individual deciles

### Plot by quantile method
```{r, fig.height=4, fig.width=8}
load(file = "./data/sim_fp_apd_pval_bbr9.RData")
p <- plot_fp_apd_ind(simres, plot.title, alpha.val)
p
#ggsave(filename = "./figures/fig_fp_apd_ind_bbr9.pdf", width = 8, height = 4)
```

### Plot by sample size
```{r, fig.height=8, fig.width=8}
p <- plot_fp_apd_ind_n(simres, plot.title, alpha.val)
p
#ggsave(filename = "./figures/fig_fp_ind_n_bbr9.pdf", width = 8, height = 8)
```

# Conclusion

FWER is lower than the nominal level in all situations. Type I error rate is close to the expected level at individual quantiles, particularly for central quantiles and n>20. HD and QT7 perform similarly for continuous distributions. When sampling from distributions with tied values, HD is much closer to the nominal level than QT7. FDR outperforms Hochberg in all situations.
Recommend to use HD + FDR by default.  

# Make figures for article

## FWER + FDR

Use all distributions except beta-binomial with r = 1. So we have 6 sets of results that can fit in a 3 x 2 figure.

```{r, eval=FALSE, warning=FALSE}
legend <- get_legend(p_fdr_norm + guides(color = guide_legend(nrow = 1)) + theme(legend.position = "bottom", legend.box.margin = margin(0, 0, 0, 0)))

pAB <- cowplot::plot_grid(p_fdr_norm + theme(legend.position='none'), 
                          p_fdr_lnorm + theme(legend.position='none'),
                          p_fdr_cnorm + theme(legend.position='none'), 
                          p_fdr_clnorm + theme(legend.position='none'),
                          p_fdr_pois + theme(legend.position='none'), 
                          p_fdr_bbr9 + theme(legend.position='none'),
                          labels=c("A", "B", "C", "D", "E", "F"), 
                          ncol = 2, 
                          nrow = 3,
                          rel_heights = c(1, 1, 1, 1, 1, 1), 
                          label_size = 20, 
                          hjust = -0.5, 
                          scale = 0.95,
                          align = "h")

pAB <- cowplot::plot_grid(pAB, legend,
                          labels=c("", ""), 
                          ncol = 1, 
                          nrow = 2,
                          rel_heights = c(1, 0.05), 
                          label_size = 20, 
                          hjust = -0.5, 
                          scale = 0.95,
                          align = "h") 

pAB

# save figure
ggsave(filename='./figures/fig_art_fp_apd.pdf',width=10,height=12) 
```

## Results at individual deciles: normal + contaminated lognormal
```{r, eval=FALSE, warning=FALSE}
legend <- get_legend(p_ind_norm)

cowplot::plot_grid(p_ind_norm + theme(legend.position='none'), 
                   legend,
                   p_ind_clnorm + theme(legend.position='none'),
                   NULL,
                   labels=c("A", "", "B", ""), 
                   ncol = 2, 
                   nrow = 2,
                   rel_widths = c(1, 0.3), 
                   label_size = 20, 
                   hjust = -0.5, 
                   scale = 1,
                   align = "h")

# save figure
ggsave(filename='./figures/fig_art_fp_apd_ind_norm_clnorm.pdf',width=9,height=7) 
```

## Results at individual deciles: Poisson + beta-binomial (r=1)
```{r, eval=FALSE, warning=FALSE}
legend <- get_legend(p_ind_norm)

cowplot::plot_grid(p_ind_pois + theme(legend.position='none'),
                   legend,
                   p_ind_bbr1 + theme(legend.position='none'),
                   NULL,
                   labels=c("A", "", "B", ""), 
                   ncol = 2, 
                   nrow = 2,
                   rel_widths = c(1, 0.3), 
                   label_size = 20, 
                   hjust = -0.5, 
                   scale = 1,
                   align = "h")

# save figure
ggsave(filename='./figures/fig_art_fp_apd_ind_pois_bbr1.pdf',width=9,height=7) 
```
